---
title: "Week 5 - Resampling"
author: "YOUR NAME HERE"
output: html_document
---

```{r}
library(tidymodels)
library(nycflights13)
library(discrim)
```


We will be using the add-on package [discrim](https://discrim.tidymodels.org/) to access functions to perform discriminant analysis models with parsnip. If the system prompts you to install a package, or gives you a "package not found" error,
simply run `install.packages("packagename")` once to install it.

We will be working with the two main functions `vfold_cv()` and `bootstraps()` from the `rsample` package. These can be used to create K-fold cross validation splits and bootstrapped datasets.

Below is a toy example showing what happens inside the cross validation splits

```{r}
tibble(x = 1:8) %>%
  vfold_cv(v = 4) %>%
  mutate(ids = map(splits, assessment)) %>%
  unnest(ids)
```

```{r}
tibble(x = 1:8) %>%
  vfold_cv(v = 4) %>%
  mutate(ids = map(splits, analysis)) %>%
  unnest(ids)
```

and what happens in the bootstraps

```{r}
tibble(x = 1:5) %>%
  bootstraps() %>%
  mutate(ids = map(splits, analysis)) %>%
  unnest(ids)
```

```{r}
tibble(x = 1:5) %>%
  bootstraps() %>%
  mutate(ids = map(splits, assessment)) %>%
  unnest(ids)
```

# The data set

We will be using the same `flights` data set from the [nycflights13](https://github.com/tidyverse/nycflights13) package. nycflights13 is an R data package containing all out-bound flights from NYC.

We will build a classification model that sees if any given flight is delayed or not.
Furthermore, let us trim down the number of variables we are working with. Lastly, let us select to only work with flights taken place during the first month.

```{r}
flights1 <- flights %>%
  mutate(delay = factor(arr_delay > 0, c(TRUE, FALSE),
                        c("Delayed", "On time"))) %>%
  filter(month == 1, !is.na(delay)) %>%
  select(delay, hour, minute, dep_delay, carrier, distance)
```

now that we have performed some cleaning, will we proceed to perform a train-test split.

```{r}
set.seed(1234)
flights_split <- initial_split(flights1)

flights_train <- training(flights_split)
flights_test <- testing(flights_split)
```

At this point in time, we will take the training data set and create a resampled data set using K-fold Cross validation. Notice we are going to use the training data set.

```{r}
flights_folds <- vfold_cv(flights_train, v = 10)
flights_folds
```

This tibble contains the data for each fold that we need. Now we need to define a model we want to run within each resample. We will be reusing the LDA model from the previous lab.

```{r}
lda_spec <- discrim_linear() %>%
  set_mode("classification") %>%
  set_engine("MASS")
lda_spec
```

This time we will go one step further and create a `workflow()`, this workflow is created to specify what model we want to run, and what we want to do the data set before passing it to the model

```{r}
lda_wf <- workflow() %>%
  add_formula(delay ~ dep_delay + distance) %>%
  add_model(lda_spec)
lda_wf
```

```{r}
folds_res <- fit_resamples(lda_wf, resamples = flights_folds)
```

Now that we have fitted the model within each model, we can pull out the metrics that were calculated within each resample. We will be using `collect_metrics()` to do that for us. By default it returns the aggregated results.

```{r}
folds_res %>%
  collect_metrics()
```

But that can be turned off by setting `summarize = FALSE`.

```{r}
folds_res %>%
  collect_metrics(summarize = FALSE)
```

# YOUR TURN

It is your turn, repeat what we did above, but instead of doing K-fold Cross Validation, do a 20 fold bootstrap. How do you interpret your results?
